\cvsection[page2sidebar]{Volunteer experience}

\cvevent{Team Leader -- IT and Logistics}{THS Mental Health Week}{2019}{}
As a team leader for IT and Logistics I oversaw the work for creating a website, and being GDPR compliant. As a Team Leader I trained the group in web development and React.

\cvsection{Featured Projects}

\cvevent{\printinfo{\faRocket}{semantic-release-slack-bot}}{}{April 2019}{}
A plugin for semantic-release that adds release notifications from a slack bot. It is downloaded 40 000 times a month, and is used by Xerox Interactive, SystemSeed, Elastic, and hundreds more.

\vspace{4pt}

\begin{itemize}
    \item \textbf{Technologies used:} Node, Semantic Release, Circle CI, Slack.
    \item \textbf{Project link:} github.com/juliuscc/semantic-release-slack-bot
\end{itemize}

\divider

\cvevent{\printinfo{\faSitemap}{Plutt -- Safe microfrontends without the hassle}}{}{January 2020 -- June 2020}{}
A microfrontend build tool that enables developers to generate microfrontends from framework-native components and to serve them version- and type-safely. Plutt provides: access transparency, automatic version safety, framework agnostic consumption, and type safety.

\vspace{4pt}

\begin{itemize}
    \item \textbf{Technologies used:} Node, Typescript, Oclif, React, Vue, Webpack.
    \item \textbf{Project link:} github.com/juliuscc/plutt
\end{itemize}

% \divider

% \cvevent{\printinfo{\faVolumeUp}{heos-api}}{}{December 2017}{}
% The leading npm package to control your Denon Heos smart speakers, with 500--2000 downloads a month. It is a library that enables developers to write applications in Node.js that communicates with and controls Denon Heos smart speakers.

% \vspace{4pt}

% \begin{itemize}
%     \item \textbf{Technologies used:} TypeScript, NPM, Node.js, Rollup, Jest and Travis CI.
%     \item \textbf{Project link:} github.com/juliuscc/heos-api
% \end{itemize}

\divider

\cvevent{\printinfo{\faSearch}{Simple Search Engine}}{}{October 2018}{}
A simple search engine using web crawler data from Common Crawl, to index websites and sort them. The project resulted in very successful results with an extremely small subset of the available data.

\vspace{4pt}

\begin{itemize}
    \item \textbf{Technologies used:} Spark, Hadoop, Cassandra and Scala.
    \item \textbf{Project link:} github.com/juliuscc/simple-search-engine
\end{itemize}

\divider


\cvevent{\printinfo{\faGroup}{Machine Learning Festival Simulation}}{}{December 2018}{}
A simulation project where Q-learning was used to simulate a festival. A multi-agent system was simulated and agents successfully learned how to behave for them to have a great festival experience.

\vspace{4pt}

\begin{itemize}
    \item \textbf{Technologies used:} GAMA, Machine learning, Q-learning.
    \item \textbf{Project link:} github.com/juliuscc/machine-learning-festival-simulation
\end{itemize}


\divider

\cvevent{\printinfo{\faIndustry}{craft-africa.com}}{Craft Africa}{April 2017 -- May 2017}{}

A school project where we created a website for Craft Africa (now called Wayout). We worked with Scrum during 4 weeks. I had a project management role in the group.

\vspace{4pt}

\begin{itemize}
    \item \textbf{Technologies used:} Scrum, JavaScript, Pug, SCSS, MongoDB and Express.js.
    \item \textbf{Project link:} github.com/juliuscc/craft-africa
\end{itemize}
